Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-09 paper/disc20clustering.tex
Contributions

\subsection{Our Contributions}
We provide an improved lower bound 
of $\Omega(k\cdot\ell)$ on the competitive ratio of any online deterministic online algorithm 
even in the learning model;
the best known lower bound so far was $\Omega(k)$,
even for a more general model~\cite{repartition-disc}.
We also present an asymptotically optimal, 
$O(k\cdot \ell)$-competitive algorithm
for the learning model.
For the repartitioning model, we present  
an asymptotically optimal,
$\Theta(\ell)$ algorithm for $k=3$, improving the best known upper bound 
so far $O(\ell^2)$~\cite{repartition-disc}.
Then, we present a strictly $6$-competitive algorithm for $k=2$ that improves upon previous $7$-competitive algorithm with $O(\ell^2)$ additive constant.
%
The overview of known results is in Table~\ref{tab:overview}.

>>>>

\subsection{Our Contributions}

This paper presents several new results on the dynamic graph partitioning problem  without augmentation.
Our main result is a tight bound on the general case: we present a lower bound of $\Omega(k\cdot\ell)$ on the competitive ratio of any online deterministic online algorithm 
even in the learning model.
The best known lower bound so far was $\Omega(k)$,
even for a more general model~\cite{repartition-disc}.
We also present an asymptotically optimal, 
$O(k\cdot \ell)$-competitive algorithm
for the learning model.
For the repartitioning model, we present  
an asymptotically optimal,
$\Theta(\ell)$ algorithm for $k=3$, improving the best known upper bound 
so far $O(\ell^2)$~\cite{repartition-disc}.
We further present a strictly $6$-competitive algorithm for $k=2$ that improves upon previous $7$-competitive algorithm with $O(\ell^2)$ additive constant.
%
Table \ref{tab:overview} provides an overview of our contributions compared to prior work.
